Quantum-assisted unsupervised data clustering

### 2020-05-07 manuscript.tex

In order to check that our algorithm gives the expected results we compare it to classical calculations of the distance matrix on two data sets of binary vectors, as shown in Fig.~\ref{fig:distance_matrix}.  
We see good agreement between the distance matrices calculated classically and on the IBM Q Experience. 
The theoretical calculations and classical simulations show perfect agreement with each other (Fig.~\ref{fig:distance_matrix}(a)). 
The difference between Figs.~\ref{fig:distance_matrix} (a) and (b) appears due to noise in the currently available non fault-tolerant quantum processors.

>>>>

In order to check that our algorithm gives the expected results we compare it to classical calculations of the distance matrix on two data sets of binary vectors, as shown in Fig.~\ref{fig:distance_matrix}.  
We see good agreement between the distance matrices calculated classically and on the IBM Q Experience. 
The match is close, but not perfect, and we attribute it to noise in the currently available non fault-tolerant quantum processors.
